---
title: Rolling Window Assignment
author: Alex Moyse
output: 
  html_document:
    toc: true
    toc_float: true
---


<H1> First Steps </H1>

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
library(dplyr)
library(zoo)
library(readr)
library(tidyverse)
```

<H2> Starting the Problem- A six-day rolling average on a fixed file </H2>
First Things first let's work on a singular goal of getting a six-day rolling average. 

For this we will use a function named rollmean, which handles null values as well as allows for the choice in how the window is calculated. We use right so that it's the prior days. 


```{r}
file <- "coin_Dogecoin.csv"
df <- read_delim("coin_Dogecoin.csv", delim=",", col_names=TRUE, show_col_types = FALSE)
df$Six_Day_RollingAvg <- rollmean(df$Close, 6, fill = 0, na.pad = FALSE, 
  align = c("right"),)
head(df,10)
```

<H2> Completing the Problem- A year to date average on a fixed file </H2>
After we have a six day rolling average, let's address the ytd mean. 

```{r}
file <- "coin_Dogecoin.csv"
df <- read_delim(file, delim=",", col_names=TRUE, show_col_types = FALSE)
print(df$Close[1:10])
for (row_number in 1:NROW(df)){
   df$RollingAvg[row_number] = mean(df$Close[1:row_number])
  }
df
```
<H1> Expanding the problem-Getting a list of available coins </H1>

From there, let's have some fun and get a list of all the available coins in the dataset from Kaggle. The goal of this is being able to easily select a coin from the list, and proceed to run it.

```{r}
file_list <- list.files(path="coin_list")
coin_list <- ""
print(file_list)
for (i in 1:length(file_list)){
  coin_list <- c(coin_list, str_extract_all(file_list[i], "(?<=coin_)(.*)(?=.csv)"))
}
Coin_df <- data.frame(coin_list = unlist(coin_list))
```
<H2> Coin Selection </H2>
From this list, feel free to pick any two coins

```{r}
Coin1 <- "Bitcoin" 
Coin2 <- "Ethereum"

if (!any(Coin_df$coin_list==Coin1)){
  print("Please select a different coin from the list above for Coin 1")
}
if (!any(Coin_df$coin_list==Coin2)){
  print("Please select a different coin from the list above for Coin 2")
}
if (any(Coin_df$coin_list==Coin1) && any(Coin_df$coin_list==Coin2))
{
  print("Please continue to the next steps")
}

```
<H1> Function Creation </H1>
Now we're going to take the code for a 6 day moving functions and year to date averages and make each into a function. I like seperating the functions so that can be easily reused in the future. 
```{r}
Six_Day_RollingAvg <- function(file_name){
  six_day_ravg <- read_delim(file_name, delim=",", col_names=TRUE, show_col_types = FALSE)
  six_day_ravg$Six_Day_RollingAvg <- rollmean(six_day_ravg$Close, 6, fill = 0, na.pad = FALSE, 
  align = c("right"),)
  return(six_day_ravg[c("Name","Date","Six_Day_RollingAvg")])
}
ytd_avg <- function(file_name){
ytd_avg_df <- read_delim(file_name, delim=",", col_names=TRUE, show_col_types = FALSE)
ytd_avg_df$RollingAvg <- "NA"
for (row_number in 1:NROW(ytd_avg_df)){
    ytd_avg_df$RollingAvg[row_number] = mean(ytd_avg_df$Close[1:row_number])
}
return(ytd_avg_df[c("Name","Date","RollingAvg")])
}
Make_File_from_Coin <- function(coin_name){
  return (paste0("coin_list/","coin_", coin_name ,".csv"))
  }
```

Now let's test these created functions. First things first, let's test Make_File_from_Coin to ensure that we are generating the right relative path. Next, let's create the 4 dataframes for Coin1 and Coin2, merging them together by Name and Date as we wish to create 2 dataframes, one for each Coin1 and Coin2, with the coin name, date, YTD average and rolling average. 

Finally, let's combine the two dataframes for each coin, merging on the date, so we can easily play with the data in the future. 

```{r}
print(Make_File_from_Coin(Coin1))
df_coin_1 <- merge(Six_Day_RollingAvg(Make_File_from_Coin(Coin1)), ytd_avg(Make_File_from_Coin(Coin1)), by=c("Name","Date"))
df_coin_2 <- merge(Six_Day_RollingAvg(Make_File_from_Coin(Coin2)), ytd_avg(Make_File_from_Coin(Coin2)), by=c("Name","Date"))
output <- (merge(df_coin_1, df_coin_2, by=c("Date")))
knitr::kable(head(output), "simple")
```

And we are going to test modularlly making charts here as well. 

```{r, echo=FALSE}
plot(x=output$Date, y=output$Six_Day_RollingAvg.x,
pch=18,
cex=1,
xlab="Year", ylab="Rolling Average",
main=paste0("Comparing the moving average of ", Coin1, " And ", Coin2 ),
)
lines(x=output$Date, y=output$Six_Day_RollingAvg.y)
```

<H1> The End </H1>
Finally, we have the output of the dataset, a view of the 6-day average & YTD value of the two coins per day (in this case, BTC and EOS).

<H1> References </H1>
Kaggle's Historical Crypto Set-https://www.kaggle.com/sudalairajkumar/cryptocurrencypricehistory/download
