---
title: Extra Rolling Window Assignment
author: Alex Moyse
output:
    html_document:
    toc: true
    toc_float: true
---


<H1> First Steps </H1>

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
library(dplyr)
library(zoo)
library(readr)
library(tidyverse)
```

<H2> Starting the Problem- A six-day rolling average on a fixed file </H2>
First Things first let's work on a singular goal of getting a six-day rolling average. 


```{r}
file <- "coin_Dogecoin.csv"
df <- read_delim("coin_Dogecoin.csv", delim=",", col_names=TRUE, show_col_types = FALSE)
df$Six_Day_RollingAvg <- rollmean(df$Close, 6, fill = 0, na.pad = FALSE, 
  align = c("right"),)
head(df,10)
```

<H2> Completing the Problem- A year to date average on a fixed file </H2>
After we have a six day rolling average, let's address the ytd mean. 

```{r}
file <- "coin_Dogecoin.csv"
df <- read_delim(file, delim=",", col_names=TRUE, show_col_types = FALSE)
print(df$Close[1:10])
for (row_number in 1:NROW(df)){
   df$RollingAvg[row_number] = mean(df$Close[1:row_number])
  }
df
```
<H2> Expanding the problem-Getting a list of available coins </H2>
From there, let's have some fun and get a list of all the available coins in the dataset from Kaggle. The goal of this is being able to easily select a coin from the list, and proceed to run it 

```{r}
file_list <- list.files(path="coin_list")
coin_list <- ""
print(file_list)
for (i in 1:length(file_list)){
  print(str_extract_all(file_list[i], "(?<=coin_)(.*)(?=.csv)"))
  coin_list <- c(coin_list, str_extract_all(file_list[i], "(?<=coin_)(.*)(?=.csv)"))
}
Coin_df <- data.frame(coin_list = unlist(coin_list))
```

From this list, feel free to pick any two coins

```{r}
Coin1 <- "Bitcoin" 
Coin2 <- "EOS"

if (!any(Coin_df$coin_list==Coin1)){
  print("Please select a different coin from the list above for Coin 1")
}
if (!any(Coin_df$coin_list==Coin2)){
  print("Please select a different coin from the list above for Coin 2")
}
if (any(Coin_df$coin_list==Coin1) && any(Coin_df$coin_list==Coin2))
{
  print("Please continue to the next steps")
}

```

Now we're going to take the code for a 6 day moving functions and year to date averages and make it into a function. 
```{r}
Six_Day_RollingAvg <- function(file_name){
  six_day_ravg <- read_delim(file_name, delim=",", col_names=TRUE, show_col_types = FALSE)
  six_day_ravg$Six_Day_RollingAvg <- rollmean(six_day_ravg$Close, 6, fill = 0, na.pad = FALSE, 
  align = c("right"),)
  return(six_day_ravg[c("Name","Date","Six_Day_RollingAvg")])
}
ytd_avg <- function(file_name){
ytd_avg_df <- read_delim(file_name, delim=",", col_names=TRUE, show_col_types = FALSE)
ytd_avg_df$RollingAvg <- "NA"
for (row_number in 1:NROW(ytd_avg_df)){
    ytd_avg_df$RollingAvg[row_number] = mean(ytd_avg_df$Close[1:row_number])
}
return(ytd_avg_df[c("Name","Date","RollingAvg")])
}
Make_File_from_Coin <- function(coin_name){
  return (paste0("coin_list/","coin_", coin_name ,".csv"))
  }
```

Now let's test these created functions:

```{r}
print(Make_File_from_Coin(Coin1))
df_coin_1 <- merge(Six_Day_RollingAvg(Make_File_from_Coin(Coin1)), ytd_avg(Make_File_from_Coin(Coin1)), by=c("Name","Date"))
df_coin_2 <- merge(Six_Day_RollingAvg(Make_File_from_Coin(Coin2)), ytd_avg(Make_File_from_Coin(Coin2)), by=c("Name","Date"))
output <- (merge(df_coin_1, df_coin_2, by=c("Date")))
head(output)
```
<H1> The End </H1>
Finally, we have the output of the dataset, a view of the 6-day average & YTD value of the two coins per day (in this case, BTC and EOS).

<H1> References </H1>
Kaggle's Historical Crypto Set-https://www.kaggle.com/sudalairajkumar/cryptocurrencypricehistory/download
